\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
conclusion

\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage{appendix}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}

@@

\lstset{frame=tb,
  breaklines=true,                                        % sets automatic line breaking
  language=php,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

@@

The network traffic analysis uncovered the behavior over the wire of a host infected by a strain of ransomware known as Maktub. The host exhibited signs of compromise following interaction with a mail server, indicating a malicious mail attachment was the initial point of entry. The host established a openVPN session tunneled over TLS as a likely secure communication channel to the C2. Finally, in order to provide a payment platform for victim, TOR hidden services over a .onion to the web link.

>>>>

\documentclass[11pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)
\usepackage{float}
\usepackage{sectsty}
\usepackage{appendix}
\usepackage[numbers]{natbib}
\sectionfont{\centering}
\usepackage{listings}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{fancyvrb}

@@

\lstset{frame=tb,
  breaklines=true,                                        % sets automatic line breaking
  language=php,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\RecustomVerbatimCommand{\VerbatimInput}{VerbatimInput}%
{fontsize=\footnotesize,
 %
 frame=lines,  % top and bottom rule only
 framesep=2em, % separation between frame and text
 rulecolor=\color{Gray},
 %
 label=\fbox{\color{Black}evilstats.txt},
 labelposition=topline,
 %
 commandchars=\|\(\), % escape character and argument delimiters for
                      % commands within the verbatim
 commentchar=*        % comment character
}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\VerbatimInput{evilstats.txt}

@@

The network traffic analysis uncovered the behavior over the wire of a host infected by a strain of ransomware known as Maktub. The host exhibited signs of compromise following interaction with a mail server, indicating a malicious mail attachment was the initial point of entry. The host established a openVPN session tunneled over TLS as a likely secure communication channel to the C2. Finally, in order to provide a payment platform for victim, the attackers used TOR hidden services over a .onion to the web link. These domains obtained via DNS quiries provided the final pieces in understanding the malware's bahavior and laying attribution to the Maktub locker.
